

%%%% answer to referee report 14 June 2022

\documentclass[a4paper,10pt]{article}      
\usepackage[utf8x]{inputenc}
\pdfoutput=1
\usepackage{nccfoots}
\renewcommand\refname{Referencias}
\usepackage{times}
\usepackage{geometry}
\usepackage[T1]{fontenc}
\usepackage{color}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{array}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{setspace}
\usepackage{stmaryrd}
\usepackage{marginnote}
\usepackage[mathscr]{euscript}
\usepackage{subfigure}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage[dvips]{epsfig}
%\usepackage{showkeys}
\usepackage{wasysym}
\usepackage{mathrsfs}
\usepackage{eufrak}
\usepackage{bm}
\usepackage{authblk}
\usepackage{slashed}
\usepackage{yhmath} 
%\usepackage{authblk}
%%%%%large commented parts
\usepackage{verbatim}
\renewcommand\Affilfont{\itshape\small}

\usepackage{natbib}


\theoremstyle{plain}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{assumption}{Assumption}
\newtheorem*{conjecture}{Conjecture}
\newtheorem*{subconjecture}{Subconjecture}
\newtheorem{corollary}{Corollary}
\newtheorem{main}{Main Result}
\newtheorem*{definition}{Definition}
\newtheorem*{remark}{Remark}



\usepackage{tikz}
\usetikzlibrary{arrows}

\newcommand{\myrule} [3] []{
    \begin{center}
        \begin{tikzpicture}
            \draw[#2-#3, ultra thick, #1] (0,0) to (0.5\linewidth,0);
        \end{tikzpicture}
    \end{center}
}


% Underlined lowcase latin letters
\def\es{{\bar{s}}}
\def\er{{\bar{r}}}

% Boldface mathmode lowcase latin letters
\def\bma{{\bm a}}
\def\bmb{{\bm b}}
\def\bmc{{\bm c}}
\def\bmd{{\bm d}}
\def\bme{{\bm e}}
\def\bmf{{\bm f}}
\def\bmg{{\bm g}}
\def\bmh{{\bm h}}
\def\bmi{{\bm i}}
\def\bmj{{\bm j}}
\def\bmk{{\bm k}}
\def\bml{{\bm l}}
\def\bmn{{\bm n}}
\def\bmm{{\bm m}}
\def\bmo{{\bm o}}
\def\bmp{{\bm p}}
\def\bms{{\bm s}}
\def\bmt{{\bm t}}
\def\bmu{{\bm u}}
\def\bmv{{\bm v}}
\def\bmw{{\bm w}}
\def\bmx{{\bm x}}
\def\bmy{{\bm y}}
\def\bmz{{\bm z}}

% Boldface mathmode numbers
\def\bmzero{{\bm 0}}
\def\bmone{{\bm 1}}
\def\bmtwo{{\bm 2}}
\def\bmthree{{\bm 3}}

% Boldface mathmode uppercase latin letters
\def\bmA{{\bm A}}
\def\bmB{{\bm B}}
\def\bmC{{\bm C}}
\def\bmD{{\bm D}}
\def\bmE{{\bm E}}
\def\bmF{{\bm F}}
\def\bmG{{\bm G}}
\def\bmH{{\bm H}}
\def\bmK{{\bm K}}
\def\bmL{{\bm L}}
\def\bmM{{\bm M}}
\def\bmN{{\bm N}}
\def\bmP{{\bm P}}
\def\bmQ{{\bm Q}}
\def\bmR{{\bm R}}
\def\bmS{{\bm S}}
\def\bmT{{\bm T}}
\def\bmX{{\bm X}}
\def\bmZ{{\bm Z}}

\def\Riem{{\bm R}{\bm i}{\bm e}{\bm m}}
\def\Ric{{\bm R}{\bm i}{\bm c}}
\def\Weyl{{\bm W}{\bm e}{\bm y}{\bm l}}
\def\Schouten{{\bm S}{\bmc}{\bm h}}

% Mathbf letters
\def\mbfu{\mathbf{u}}

% Boldface mathmode lowcase greek letters
\def\bmalpha{{\bm \alpha}}
\def\bmbeta{{\bm \beta}}
\def\bmgamma{{\bm \gamma}}
\def\bmdelta{{\bm \delta}}
\def\bmepsilon{{\bm \epsilon}}
\def\bmeta{{\bm \eta}}
\def\bmzeta{{\bm\zeta}}
\def\bmxi{{\bm \xi}}
\def\bmchi{{\bm \chi}}
\def\bmiota{{\bm \iota}}
\def\bmomega{{\bm \omega}}
\def\bmlambda{{\bm \lambda}}
\def\bmmu{{\bm \mu}}
\def\bmnu{{\bm \nu}}
\def\bmpi{{\bm \pi}}
\def\bmpsi{{\bm \psi}}
\def\bmphi{{\bm \phi}}
\def\bmvarphi{{\bm \varphi}}
\def\bmsigma{{\bm \sigma}}
\def\bmvarsigma{{\bm \varsigma}}
\def\bmtau{{\bm \tau}}

% Boldface mathmode uppercase greek letters
\def\bmUpsilon{{\bm \Upsilon}}
\def\bmSigma{{\bm \Sigma}}

% Boldface operators
\def\bmpartial{{\bm \partial}}
\def\bmnabla{{\bm \nabla}}
\def\bmhbar{{\bm \hbar}}
\def\bmperp{{\bm \perp}}


%Yang-Mills indices
\def\fraka{\mathfrak{a}}
\def\frakb{\mathfrak{b}}
\def\frakc{\mathfrak{c}}


%Counter variable for the margin notes
\newcounter{mnotecount}%[section]

% This code generates the margin notes
\newcommand{\mnotex}[1]%{}
{\protect{\stepcounter{mnotecount}}$^{\mbox{\footnotesize $\bullet$\themnotecount}}$ 
\marginpar{%\color{red}%
\raggedright\tiny\em
$\!\!\!\!\!\!\,\bullet$\themnotecount: #1} }


\renewcommand{\title}[1]{{\bfseries #1}\par}
\renewcommand{\author}[1]{\medskip{#1}\par\smallskip}
\newcommand{\affiliation}[1]{{\itshape #1}\par}
\newcommand{\email}[1]{E-mail:~\texttt{#1}\par}


\numberwithin{equation}{section}




\begin{document}
\begin{center}
  \title{\LARGE Response to the referee report on ``The conformal Killing spinor initial data equations''
  \\ \vspace{0.5cm} \Large
  }
\vspace{3mm}
\author{\large }
%\Footnotetext{}{1991 \emph{Mathematics Subject Classification.} 58J45,53C25,83C05.}
%\Footnotetext{}{\emph{Key words and phrases.} Nonlinear Stability, General Relativity, Einstein metrics, Einstein flow.}

\vspace{1mm}
%\affiliation{Universität Potsdam, Institut für Mathematik\\Am Neuen Palais 10\\14469 Potsdam, Germany} 
%\email{klaus.kroencke@uni-potsdam.de} 
\end{center}

%\begin{center}
%\today
%\end{center}
%
\vspace{2mm}

 
%
%\begin{center}
%\line(1,0){250}
%\end{center}
% \myrule[double]{}{}
%
%\tableofcontents
%

We thank the referee for his/her valuable the time taken
for the careful reading our paper and for the insightful comments. We think that the article has significantly improved
with the received recommendations. We have addressed the comments of the referee and we provide a list of the changes for so that
they can be more easily located in the revised version the paper which we adjoin.


  \begin{itemize}

  \item[i)] About Comment 1. Indeed we agree with the referee that the
    fact that $\xi_{AA'}$ is not a Killing vector is a conceptual
    important point to stress and explained in the text as early as
    possible. To do so, we have added some text at the top of page 6 
    in the revised draft ---see equations (9) and (10), also.
  
     
  \item[ii)] About Comment 2: We agree with the referee that at
    first sight equations (19) and (45) do not imply that $B_{ABC}$
    and $B_{ABCD}$ vanish on the conformal boundary, directly. By
    continuity, it is clear that they must vanish, however; some text to this
    effect has been added to the bottom of section 3.1. We have also 
    performed the suggested calculation, given in Remark 5, which
    allows one to conclude this without the continuity argument in the 
    case of non-null conformal boundary. See also the end of Section 4.1
    for a comment regarding the valence 2 case.
     We thank the referee for this comment and for suggesting a solution as
    well. 

  \item[iii)] About Comment 3: We thank the referee for pointing out
    this fact about the 2-dimensional Sen connection. In the case that the
    normal takes the "canonical" form given in equation (84) ---i.e. $l^a+n^a$---
     in terms of the 
    Petrov-adapted spin dyad, the $\lambda, \sigma$ coincide with the NP 
    scalars (see Remark 12) and we agree that there are links with the 2-dimensional
    Sen connection with respect to the vector $l^a-n^a$. However, in the more general case, 
    where the normal is not of the canonical form with respect to the Petrov-adapted dyad, 
    it is not clear to us
     what the link should be and so we have
    opted to leave this for future work. Some text has been added to clarify
    the relation between the 4-dimensional NP scalars and the connection coefficients with respect
    to the Petrov-adapted dyad
     ---see Remark 12 (added) and the text of Appendix A.2.

    
  \end{itemize}






\end{document}


